\section{Documented Assumptions}
\label{sec:assumptions}

% Mandatory. Model assumptions, grouped by entity, schedule, routing/resources and yields.
The model represents one process-batch as a single agent. The production plan
gives each batch as \SI{150}{\kilo\gram} of pre-weighed active-ingredient powder
blend, and \SI{75}{\kilo\gram} of excipients is added in premix, so a batch
weighs \SI{225}{\kilo\gram}. With \SI{500}{\milli\gram} active and
\SI{250}{\milli\gram} excipient in each \SI{750}{\milli\gram} tablet, one batch
gives \num{300000} tablets before yield losses
($\text{tablets} = \text{kg}_{\text{active}} \times 2000$). Batches never mix,
because of full traceability, so each batch stays a separate entity from start
to end.

The time unit is hours and the horizon is the five-day plan. The run is
terminating and stops when the last batch is shipped. Arrivals follow the
\texttt{Plan} table exactly: 50 batches over 1--5 July, ten per day, with a mix
of 17 CoreTab, 18 PlusTab and 15 MaxTab.

For routing and resources we make the following assumptions. Premix sends each
batch to whichever unit, old or new, is free, and a failure during processing
scraps the whole batch. CoreTab skips coating, while PlusTab and MaxTab are
coated. Packaging is rate-based at \SI{30000}{tablets/hour} per line, and
leftover tablets that cannot fill a full bottle are scrapped. One shared
\texttt{cleaningTeam} of capacity one performs all cleaning, setup, changeover
and repairs through a seize-delay-release logic, which is why these activities
compete for the same resource.

The yield assumptions are premix Triangular(98.5\%, 99\%, 99.5\%), a baseline
press scrap of \SI{10}{\percent}, packaging Triangular(99\%, 99.5\%, 99.8\%) and
a drying yield of \SI{100}{\percent}. Repairs and the cleaning team start empty
and idle in each simulated week. The dryer queue uses FIFO discipline
(\texttt{queueStrategy}~$=0$) in the baseline; the EDD and SPT alternatives are
tested in Section~\ref{sec:experiments} and leave throughput unchanged, because
the drying times are near-homogeneous ($\sigma\approx\SI{0.39}{\hour}$).
