\section{Conclusions and Insights}
\label{sec:conclusions}

% ~0.75 page. Managerial takeaways, tied to the KPIs.
The baseline identifies drying as the primary constraint, at \SI{94.3}{\percent}
utilisation and with the highest required unit-hours. The cleaning team is second
at \SI{79.6}{\percent}, and packaging, although it has the largest absolute
workload, is only third at \SI{52.4}{\percent} because it runs on three parallel
lines. At the current 50-batch order book no capacity lever raises throughput: a
second dryer relieves drying but moves the bottleneck onto the cleaning team
(\SI{79.6}{\percent} to \SI{95.0}{\percent}), since each dryer adds a two-hour
clean, and adding cleaning staff then pushes the constraint onto packaging.
Shipped output holds at \numrange{60000}{61000} bottles in every case, because
volume is fixed by the plan and per-batch yield, not by station capacity; the
$2^3$ factorial confirms that no effect, main or interaction, is significant.

Towards 2030 we grow the order book itself, to 75 and 100 batches. The line
\emph{produces} the higher volume (60{,}494 to 123{,}496 bottles) but does not
absorb it: the single dryer saturates (\SI{94.3}{\percent} to \SI{96.8}{\percent}),
mean flow time roughly doubles (179 to 338 h), WIP nearly doubles, and on-time
delivery collapses from \SI{100}{\percent} to \SI{54}{\percent}. Capacity additions
at volume shift the constraint but barely recover service: a second dryer plus a
larger cleaning team still leave the team near \SI{96}{\percent} and flow at 327 h.
The dryer-and-clean coupling on the shared team is a structural limit that more
machines relocate rather than remove; restoring 2030 service needs the dryer clean
decoupled from the shared team (a dedicated or faster clean), not just one more
machine.

For shipped output the decisive lever is Industry~4.0. Predictive maintenance at
the press, where sensors catch force or fill-depth drift before it scraps tablets,
cuts scrap from \SI{10}{\percent} to \SI{4}{\percent} and raises throughput by
4{,}842 bottles per run ($+\SI{8.0}{\percent}$, 95\% CI $[3{,}543,\,6{,}141]$),
the only lever that does so and the cheapest, needing only a sensor retrofit. Our
recommendation is therefore twofold: at today's volume, defer the line capital
expansion and invest in the press-sensor scrap reduction; and before 2030 volume
materialises, address the dryer-clean coupling directly, since simply adding a
dryer only moves the bottleneck to the cleaning team.
